---
title: "1_3_summarizing_jensen_files.Rmd"
author: "Aspen Coyle"
date: "2/10/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

This is a summary of the available samples that the Roberts lab (to the best of our knowledge) has available to us.

```{r libraries, message=FALSE, warning=FALSE}
# Add all required libraries here
list.of.packages <- c("tidyverse", "rnaturalearth", "rnaturalearthdata", "sf", "rgeos")
# Get names of all required packages that aren't installed
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[, "Package"])]
# Install all new packages
if(length(new.packages)) install.packages(new.packages)


# Load all required libraries
lapply(list.of.packages, FUN = function(X) {
  do.call("require", list(X))
})
```




## Describing Potential Spatial Examinations (Hematodinium-only)

For this, we only care about samples that are definitively positive for _Hematodinium_ infections, as determined by PCR.



```{r}
# Read in data on Hematodinium infections
hemat.dat <- read.delim(file = "../analyses/jensen_cleaned_data/relevant_sample_data.txt")


# Filter out samples that aren't positive for Hematodinium
hemat.dat <- hemat.dat %>%
  dplyr::filter(BCS_PCR_results == 1)

# Produce map of Hematodinium-positive samples
world <- ne_countries(scale = "medium", returnclass = "sf")
ggplot(data = world) +
  geom_sf() +
  geom_count(data = hemat.dat, aes(x = Longitude, y = Latitude), shape = 23, fill = "red", position = "jitter") +
  coord_sf(xlim = c(-180, -120), ylim = c(50, 70), expand = FALSE) +
  scale_size_area()

# Produce map of Hematodinium-positive samples in Bering Sea area
ggplot(data = world) +
  geom_sf() +
  geom_count(data = hemat.dat, aes(x = Longitude, y = Latitude), shape = 23, fill = "red", position = "jitter") +
  coord_sf(xlim = c(-179, -155), ylim = c(50, 67), expand = FALSE) +
  scale_size_area()

# Produce map of Hematodinium-positive samples in GOA area
ggplot(data = world) +
  geom_sf() +
  geom_count(data = hemat.dat, aes(x = Longitude, y = Latitude), shape = 23, fill = "red", position = "jitter") +
  coord_sf(xlim = c(-161, -151), ylim = c(56, 59), expand = FALSE) +
  scale_size_area()


# Produce map of Hematodinium-positive samples in GOA area
ggplot(data = world) +
  geom_sf() +
  geom_count(data = hemat.dat, aes(x = Longitude, y = Latitude), shape = 23, fill = "red", position = "jitter") +
  coord_sf(xlim = c(-161, -151), ylim = c(56, 59), expand = FALSE) +
  scale_size_area()

# Produce map of Hematodinium-positive samples in SE AK area
ggplot(data = world) +
  geom_sf() +
  geom_count(data = hemat.dat, aes(x = Longitude, y = Latitude), shape = 23, fill = "red", position = "jitter") +
  coord_sf(xlim = c(-141, -121), ylim = c(50, 65), expand = FALSE) +
  scale_size_area()

# Produce summary table of general location
table(hemat.dat$General_Location)

# Produce summary table of specific location
table(hemat.dat$Specific_Location, useNA = "ifany")

# Produce summary table of both
table(hemat.dat$General_Location, hemat.dat$Specific_Location)

# Produce summary table of year
table(hemat.dat$Year)

table(hemat.dat$Year, hemat.dat$General_Location)

table(hemat.dat$Species_Name, hemat.dat$General_Location)

ber.dat <- hemat.dat %>%
  filter(General_Location == "BS")

table(ber.dat$Year, ber.dat$Species_Name)

hemat.dat %>%
  filter(Latitude > 63.5) %>%
  NROW()

#### CHOOSE TANNER CRAB SAMPLES TO EXAMINE ---------------------
inf_tanner.dat <- hemat.dat %>%
  filter(Species_Name == "Chionoecetes bairdi")

table(inf_tanner.dat$Year, inf_tanner.dat$General_Location)

snow.dat <- hemat.dat %>%
  filter(Species_Name == "Chionoecetes opilio")

table(snow.dat$Year, snow.dat$General_Location)

table(inf_tanner.dat$Year, inf_tanner.dat$General_Location)

table(snow.dat$Year, snow.dat$General_Location)

table(crab.dat$Species_Name)


```


## Examination of crab samples

```{r}
crab.dat <- read.delim(file = "../output/jensen_cleaned_data/relevant_sample_data.txt")

tanner.dat <- crab.dat %>%
  filter(Species_Name == "Chionoecetes bairdi")

snow.dat <- crab.dat %>%
  filter(Species_Name == "Chionoecetes opilio")

table(tanner.dat$Year, tanner.dat$General_Location)

table(snow.dat$Year, snow.dat$General_Location)

table(crab.dat$Species_Name)

```


## Created Tanner crab sampling list

Read in the file of our planned sampling pattern

Format is Total Crabs (Infected)
So, for instance, if a year/location combo has 100 samples and 50 are infected, it'd be 100 (50)

This isn't really proper, but is readable, and this is for a presentation anyways.

```{r}
plan.dat <- read.delim(file = "../data/planned_sampling_all_2021_03_02.csv",
                       sep = ",")

plan.dat

inf.plan.dat <- read.delim(file = "../data/planned_sampling_inf_2021_03_02.csv",
                           sep = ",")

inf.plan.dat
```

